---
title: "RIBS_EDD_processing"
author: "Gavin Lemley"
date: "January 11, 2019"
output: html_document
---

## R Markdown

Find the R-project root directory to simplify file path designations.
```{r}
root.dir <- rprojroot::find_root("raw_processing.Rproj")
```


Main process: 
1) Loads in EDD components from each folder contained in the target directory. 
2) Adds SiteID and DEC_sampletype fields to each Sample_v3.
3) Merges TestResultQC_v3 and Sample_v3 files together for each EDD set.
```{r}

folder_list <- list.files(path = file.path(root.dir, "data_input", "2017minnewaska"))
nfolder_list = length(folder_list)
RSfile_list <- list()
RSfile_list.sample <- list()

i=1
for (i in 1:nfolder_list){
  print(folder_list[i])
  input.i <- file.path(root.dir, "data_input", "2017minnewaska", folder_list[i])
  output.i <- file.path(root.dir, "data_output")
  
  temp_result <- read.table(file.path(input.i,"TestResultQC_v3.txt"),
                                      sep=",",fill=TRUE,header=FALSE,stringsAsFactors=FALSE,
                    col.names = c("sys_sample_code","lab_anl_method_name","analysis_date","fraction","column_number",
                                  "test_type","lab_matrix_code","analysis_location","basis","container_id","dilution_factor",
                                  "prep_method","prep_date","leachate_method","leachate_date","lab_name_code","qc_level",
                                  "lab_sample_id","percent_moisture","subsample_amount","subsample_amount_unit","analyst_name",
                                  "instrument_id","comment","preservative","final_volume","final_volume_unit","cas_rn","chemical_name",
                                  "result_value","result_error_delta","result_type_code","reportable_result","detect_flag",
                                  "lab_qualifiers","validator_qualifiers","interpreted_qualifiers","validated_yn",
                                  "method_detection_limit","reporting_detection_limit","quantitation_limit","result_unit",
                                  "detection_limit_unit","tic_retention_time","minimum_detectable_conc","counting_error","uncertainty",
                                  "critical_value","validation_level","result_comment","qc_original_conc","qc_spike_added",
                                  "qc_spike_measured","qc_spike_recovery","qc_dup_original_conc","qc_dup_spike_added",
                                  "qc_dup_spike_measured","qc_dup_spike_recovery","qc_rpd","qc_spike_lcl","qc_spike_ucl","qc_rpd_cl",
                                  "qc_spike_status","qc_dup_spike_status","qc_rpd_status","lab_sdg")
                    )
 
   ### ABOVE BRINGS IN FACTOR AS LOGICAL. Below converts all "T"s to "TRUE"s. May want to specify all column classes instead.  ###
   temp_result$fraction <- as.character(temp_result$fraction)
   temp_result$fraction <- plyr::revalue(temp_result$fraction, c("TRUE" = "T"))
   
  temp_sample <- read.table(file.path(input.i,"Sample_v3.txt"),
                            sep=",",fill=TRUE,header=FALSE, stringsAsFactors=FALSE,
                    col.names = c("#data_provider","sys_sample_code","sample_name","sample_matrix_code","sample_type_code",
                                  "sample_source","parent_sample_code","sample_delivery_group","sample_date","sys_loc_code",
                                  "start_depth","end_depth","depth_unit","chain_of_custody","sent_to_lab_date","sample_receipt_date",
                                  "sampler","sampling_company_code","sampling_reason","sampling_technique","task_code",
                                  "collection_quarter","composite_yn","composite_desc","sample_class","custom_field_1","custom_field_2",
                                  "custom_field_3","comment"))

  ### Creating new fields: SiteID and DEC_sample_type ###
  
  # Generate site IDs for field data by pulling info from sample_name before 3rd "-".
  temp_sample$SiteID <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N", 
                               sub("^(([^-]*-){2}[^-]*).*","\\1" , temp_sample$sample_name), NA)
  # Generate DEC_sample_type column and and populate with EB code as needed.
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" &
                                          grepl("EB",temp_sample$sample_name),"EB", NA)
  # Populate DEC_sample_type for duplicate samples as needed.
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" &
                                          grepl("DUP",temp_sample$sample_name),"DUP",temp_sample$DEC_sample_type)

    
  # Populate DEC_sample_type for N_DUPPARENT cells by locating DUP samples and finding parent sample. 
      # Accounts for different DUP variants (" DUP"", "-DUP", "WSDUP")
      # Cleaner way to do this???

  dup.vec <- temp_sample$sample_name[temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" 
                                     & grepl(" DUP", temp_sample$sample_name)]
  parent.vec <- gsub(" DUP", "", dup.vec)
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" 
                                         & temp_sample$sample_name %in% parent.vec,"N_DUPPARENT",temp_sample$DEC_sample_type)
  
  dup.vec <- temp_sample$sample_name[temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N"
                                     & grepl("-DUP", temp_sample$sample_name)]
  parent.vec <- gsub("-DUP", "", dup.vec)
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" 
                                         & temp_sample$sample_name %in% parent.vec,"N_DUPPARENT",temp_sample$DEC_sample_type)
  
  dup.vec <- temp_sample$sample_name[temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N"
                                     & grepl("WSDUP", temp_sample$sample_name)]
  parent.vec <- gsub("WSDUP", "WS", dup.vec)
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N"
                                         & temp_sample$sample_name %in% parent.vec,"N_DUPPARENT",temp_sample$DEC_sample_type)
  
  dup.vec <- temp_sample$sample_name[temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N"
                                     & grepl("WDUP", temp_sample$sample_name)]
  parent.vec <- gsub("WDUP", "W", dup.vec)
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N"
                                         & temp_sample$sample_name %in% parent.vec,"N_DUPPARENT",temp_sample$DEC_sample_type)
  
  # Populate remaining DEC_sample_type cells for field data with "N" for normal samples.
  temp_sample$DEC_sample_type <- ifelse(temp_sample$sample_source == "Field" & temp_sample$sample_type_code == "N" &
                                          is.na(temp_sample$DEC_sample_type),"N",temp_sample$DEC_sample_type)


  # Convert all NAs in temp_sample$DEC_sample_type to avoid subsetting issues in QAQC script (found that bracket subsetting in a column that contains NAs returns NA rows)
  temp_sample$DEC_sample_type[is.na(temp_sample$DEC_sample_type)] <- "Lab"
  
  # Must merge by sys_sample_code and not sample_name in order to appropriately associate MS, dissolved samples (sometimes "Diss" or "S" added to end of sys_sample_code), and other lab samples with appropriate results.
  temp_RSmerge <- merge(temp_result,temp_sample,by="sys_sample_code", all=TRUE)

  filenm <- file.path(output.i,
                      paste(folder_list[i],"_RSmerge.csv", sep=""))
  # print(filenm)

  if ((nrow(temp_result)) < (nrow(temp_RSmerge))) {
    stop('SCRIPT STOPPED: Extra records created in merge. Check EDD for errors.')
  }
  if ((nrow(temp_result)) > (nrow(temp_RSmerge))) {
    stop('SCRIPT STOPPED: Not enough records created with merge. Check for errors.')
  }

  # Create name using EDD and added suffix, and assign to current data frame
  mergenm <- paste0(folder_list[i], "_RSmerge")
  mergefile <- assign(mergenm, temp_RSmerge)
  # Do the same for only sample file data for troubleshooting
  mergenm.sample <- paste0(folder_list[i], "_Samplemerge")
  mergefile.sample <- assign(mergenm, temp_sample)

  #Add current data frame to the list of all dataframes
  RSfile_list[[i]] <- mergefile
  RSfile_list.sample[[i]] <- mergefile.sample

  # Export each merged EDD as CSVs (optional)
  # write.table(temp_RSmerge, file=filenm,sep=",", row.names = FALSE)
    
}
```

Bind all data frames (merged EDDs) in "list of data frames" together into a single data frame and write to a CSV.
```{r}
# setwd(ouput_dir)
RIBSdata = do.call(rbind, RSfile_list)
RIBSdata.sample = do.call(rbind, RSfile_list.sample)

write.table(RIBSdata, file= file.path(root.dir, "data_output", "2017-Minnewaksa_EDD-merge-bind_2-11-19.csv"),sep=",", row.names = FALSE)
write.table(RIBSdata.sample, file= file.path(root.dir, "data_output", "2017-Minnewaksa_SAMPLE_merge-bind_2-11-19.csv"),sep=",", row.names = FALSE)

```

